\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control for Energy and Thermal Comfort Optimization in Building Energy Systems using Random Forests}

### 2018-01-18 paper/final/Response_to_reviewers/Response_to_reviewers.tex

\end{itemize}

The following are itemised lists of the authors' response to the Reviewers and to the Associate Editor.

\section{Response to Associate Editor}

	\item \textbf{Associate Editor:} \textit{An updated and complete literature review should be conducted.}

	\textbf{Authors:} We performed a deep literature review. In particular, in Table 1 we classify the related work and then emphasise the novelty of our research.

	\item \textbf{Associate Editor:} \textit{The relevance to Applied Energy should be enhanced with the considerations of scope and readership of the Journal.  The present form has little relevance to APEN which might suit better for another journal. Authors must address and enhance the relevance to Applied Energy otherwise, they can consider to publish in another journal.}

	\textbf{Authors:} Following the Associate Editor and reviewers comments, we re-wrote the title and the introduction of the paper focusing on the relevance of the paper to APEN. In particular, we emphasise that...EXPLAIN HERE AS IN INTRODUCTION

@@

	\textbf{Authors:} Following the Associate Editor and reviewers comments, we re-wrote the title and the introduction of the paper focusing on the relevance of the paper to APEN. In particular, we emphasise that...EXPLAIN HERE AS IN INTRODUCTION

	\item \textbf{Associate Editor:} \textit{A proof reading by a native English speaker should be conducted to improve both language and organization quality. }

	\textbf{Authors:} We deeply revised the paper to improve both language and organization quality.

	\item \textbf{Associate Editor:} \textit{The originality of the paper needs to be further clarified. The present form does not have sufficient results to justify the novelty of a high quality journal paper. The results should be further elaborated to show how they could be used for the real applications.}

	\textbf{Authors:} We clarify in the introduction and in Section ??? the originality of the paper and how are results can be used for real applications. In particular, we emphasise that...EXPLAIN HERE AS IN INTRODUCTION

	\item \textbf{Associate Editor:} \textit{}

	\textbf{Authors:} ???

@@

\end{enumerate}

\section{Response to Reviewer 1}

\item \textbf{Reviewer 1:} \textit{This paper presents a new framework called data predictive control which integrates machine learning and model predictive control to derive the optimal online control decisions. The framework is then applied to study several demand response problems in energy area as case studies. The problem considered in this paper is important, and the proposed approach is a good initial attempt to address the problem relying on heuristics.}

\textbf{Authors:} We thank the reviewer for the comments on the problem and approach of our paper.

@@

		\item add another section to show how the previous point simplifies using data-driven methods

	\end{itemize}

\item \textbf{Reviewer 1:} \textit{Another point is that in traditional state space model, one cannot measure everything except input and output in most cases. How could we obtain such training data if these data are not measurable.}

\textbf{Authors:} We thank the reviewer for this comment, indeed our previous presentation of the paper was unclear on this fundamental aspect. In our revision we widely illustrate in the Introduction how in traditional state-space models part of the state is measurable (i.e. room temperatures, etc) and part is not measurable (i.e. layers/windows temperatures, etc). In our approach, of course, $(X^c, X^d, Y)$ are ALL measurable variables, i.e. variables that are present in the historical data of a building. The unmeasurable variables of the traditional state-space models are not assumed to be measurable in this paper, yet our prediction works well since we compensate via the regression tree/random forest approaches.

@@

\item \textbf{Reviewer 1:} \textit{The key intuition of the proposed framework is Eq. (1). It would be much better if the authors can explain their framework using Eq. (1) directly first instead of using another set of notations such as $(X^c, X^d, Y)$.}

\textbf{Authors:} We agree with the reviewer. Following this comment, and also other comments, we re-wrote the corresponding Section to make it more clear and complete to descrive the DPC technical approach. In particular...

@@

\section{Response to Reviewer 2}

\begin{enumerate}

\item \textbf{Reviewer 2:} \textit{The paper applies a recently developed concept, data predictive control (DPC) to building energy control. Models based on decision trees and random forests are applied. The efficacy of the approach appears well validated.}

\textbf{Authors:} We thank the Reviewer for the comment on our validation of the efficacy of our approach.

@@

\item \textbf{Reviewer 2:} \textit{The title is a bit confusing as it's very general. It should be changed to be more specifically focusing on the applications in this paper.}

\textbf{Authors:} We agree with the Reviewer. In the beginning, we had chosen a more general title because we believe that our approach has the potential to be applied not only to building management, but also to other application domains. However, as in this paper we develop our techniques focusing and experimenting in building management (which is indeed a core topic of APEN) we changed the title in "???".

@@

\item \textbf{Reviewer 2:} \textit{Also, novelties beyond what's in [9] - [12] should be clarified.}

\textbf{Authors:} In the introduction of the revised version we widely discuss that in this paper we improved the preliminary results obtained in [9-12] and adapted them to be applicable to the building automation use-case presented in section ???.

@@

\item \textbf{Reviewer 2:} \textit{In (1) and 2.1, the description of separation of variables is vague and needs to be more precise. E.g., the line below (1) does not make sense. It is not until later seeing the examples the meaning of this part becomes clearer. Such confusion persists up to and beyond (3). Mathematically, (2) and (3) cannot be simultaneously true. While I can see the authors trying to be descriptive, the descriptions lack rigor.}

\textbf{Authors:}  We agree with the reviewer. Following this comment, and also other comments, we re-wrote the corresponding Section to make it more clear and complete to descrive the DPC technical approach. In particular...

\item \textbf{Reviewer 2:} \textit{The main optimization problems (4) and (7) are not clear in themselves. As you look ahead to do DPC, does each future time slot have a different linear model, depending on future non-manipulative states? Then, do you assume you know precisely all the future non-manipulative states? If so, can you justify this? Apparently, with a little error in predicting of the future states, a completely different linear model may be chosen. Will this change the performance significantly? Even with forests this is a major concern.}

\textbf{Authors:} We thank the reviewer for rising this important issue. Yes, we assume that at time $k$ we know the future non-manipulative states (namely external temperature, radiation, etc.) for the Model Predictive Control time horizon, namely for the next 40 minutes. In the revised version of this paper, to answer the reviewer comment, we justify this assumption and show that, even with a large error in predicting the future states, the performance does not change significantly. Forests?? More precisely, we:

	\begin{itemize}

		\item Cite study that shows that short term predictions are extremely reliable and say there is a trade-off between the prediction accuracy and the horizon N;

		\item Provide a simulation (as for example with the bilinear model) where we inject a noise into the disturbance and show that it works as well.

	\end{itemize}

@@

\item \textbf{Reviewer 2:} \textit{In Fig. 6b, what's the difference between blue and yellow, as they seem to completely overlap?}

\textbf{Authors:} Achin?

\item \textbf{Reviewer 2:} \textit{Also, what is new in section 5 compared with section 4? Even though a real house is claimed to be used, it's still tested using simulations and energyplus, like in the previous sections. A real world experiment on this house would be much more interesting.}

\textbf{Authors:} Francesco?

%\bibliographystyle{plain}

%\bibliography{mcnbib}

\end{document}

### 2018-01-18 paper/final/casestudyReal.tex
Introduction and noisy forecast

We ran DPC with $3$ different sets of parameters $Q$, $\lambda_{min}$ and $\lambda_{max}$. Each set allows a different level of temperature bounds violation. In particular, we considered a small ($Q=100$, $\lambda_{min}=3000$ and $\lambda_{max}=100$), a medium ($Q=100$, $\lambda_{min}=1000$ and $\lambda_{max}=100$) and a large ($Q=100$, $\lambda_{min}=100$ and $\lambda_{max}=100$) violation configuration.
\paragraph{Result 1} The comparison for temperature and input schedule obtained allowing small bound violations in DPC is shown in Figure \ref{F:comparison_small}. For sake of clarity, the simulation period is restricted to $4$ days and a half, from May $1$, $2016$ $00am$ to May $5$, $2016$ $1pm$. We can see that the temperature controlled with DPC does not violate the bounds and if it does then the violation is approximately $0.1\,\degree C$. Bang-bang control also presents small bounds violations due to its working principle. We can see how the DPC control law requires the heating system to be ON for less time than the bang-bang one to keep the temperature in the comfort range. 
We will see in Figure \ref{F:comparison_all_energy_E+} that this translates to significant energy saving.

@@

%\begin{figure}[h!]
%	\begin{center}
%		\includegraphics[width=26pc]{figures/Energy_all.eps}
%	\end{center}
%	\caption{Comparison of DPC and bang-bang control performance with different violations using random forest model.}
%	\label{F:comparison_all_energy}
%\end{figure}
%An alternative comparison can be done considering the EnergyPlus model of the house for energy consumption described in Section \ref{SS:energyPlusmodel}. Results are shown in Figure \ref{F:comparison_all_energy_E+}.
In Figure \ref{F:comparison_all_energy_E+}, using the thermal energy consumption model derived in Section \ref{SS:energyPlusmodel} using EnergyPlus, we show how DPC outperforms the bang-bang controller also in terms of energy consumption and how the bounds violations allow us to save more energy. In this case, since the plot is clear and we are interested in showing energy saving on a long period, we ran the simulations over the whole testing period, i.e. $15$ days of May, from May $1$, $2016$ to May $15$, $2016$. We observe that the energy consumption associated to the bang-bang control strategy is approximately equal to $177\,kWh$. If we want to keep the temperature within a comfort range, only allowing small violations, the use of DPC produce an energy saving of $45\, kWh$, that corresponds to the $25.4\%$ over a period of $15$ days. In case of medium violations get an energy saving of $57\, kWh$, that is $32.2\%$. Instead if we allow a large violation over the same period, the energy saving is of $87\, kWh$, that corresponds to the $49.2\%$.
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=28pc]{figures/Temperatures_all.eps}
	\end{center}
	\caption{Comparison, in terms of comfort, of DPC control performance simulated over $5$ days of the testing period with $3$ different violation configurations: small, medium and large. With the large violation configuration, the temperature is almost always outside of the lower bound when this is tighter. However the maximum bound violation is less than $1\degree C$. With the small violation configuration, the temperature is always within the bound with very few exceptions. However, when it happens, the violation is lower than $0.1\degree C$. The medium violation configuration gives a temperature bound violation that is in the middle with respect to the small and the large ones.}
	\label{F:comparison_all_temperature}
\end{figure}
\begin{table}[t!]
	\centering
	%	\scalebox{0.9}{
	\begin{tabular}{cccccc}
		\toprule
		CONTROLLER  & LBV $\mathrm{MBE}$  & LBV $\mathrm{RMSE}$ & UBV $\mathrm{MBE}$ & UBV $\mathrm{RMSE}$ 	\\ 
		\midrule
		$DPC-SV$    & $0.013$             & $0.028$  			      & $0$    				 & $0$     	  	\\
		$DPC-MV$    & $0.165$ 			  & $0.146$     			  & $0$    				 & $0$		  	\\
		$DPC-LV$    & $0.410$  			  & $0.224$     			  & $0$    				 & $0$	      	\\
		$Bang-bang$ & $0.049$ 			  & $0.080$    				  & $0.0063$ 		     & $0.0120$	  	\\
		\bottomrule
	\end{tabular}
	%	}
	\caption{Lower Bound Violation (LBV) and Upper Bound Violation (UBV) errors expressed as $\mathrm{MBE}\%$ and $\mathrm{CV(RMSE)}\%$ for DPC Small Violation (DPC-SV), DPC Medium Violation (DPC-MV), DPC large Violation (DPC-LV) and bang-bang controller.}
	\captionsetup{justification=centering}
	\label{T:violationErrors}
\end{table}
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=28pc]{figures/Energy_all_EnergyPlus.eps}
	\end{center}
	\caption{Comparison of DPC and bang-bang controller performance over $15$ days of the testing period with different violation configurations, in terms of thermal energy saving using EnergyPlus model. Using bang-bang controller the house energy consumption after $15$ days is of $177kWh$. DPC with small, medium and large violation configurations allows an energy saving of $25.4\%$, $32.3\%$ and $49.2\%$ respectively.}
	\label{F:comparison_all_energy_E+}
\end{figure}

>>>>

We ran DPC with $3$ different sets of parameters $Q$, $\lambda_{min}$ and $\lambda_{max}$. Each set allows a different level of temperature bounds violation. In particular, we considered a small ($Q=100$, $\lambda_{min}=3000$ and $\lambda_{max}=100$), a medium ($Q=100$, $\lambda_{min}=1000$ and $\lambda_{max}=100$) and a large ($Q=100$, $\lambda_{min}=100$ and $\lambda_{max}=100$) violation configuration.

\textcolor[rgb]{0,0,1}{We considered 2 different simulative conditions to show the robustness of our approach:
\begin{enumerate}
	\item in Section \ref{SSS:DisturbancePerfect} we provide our simulative results considering perfect knowledge of the weather forecast;
	\item in Section \ref{SSS:DisturbanceUncertain}, to show the robustness of our methodology, we consider weather forecast subject to uncertainty. We add a gaussian noise with high variance on the perfect forecast and show that the results are close to the perfect forecast case.
\end{enumerate}
\subsubsection{Perfect knowledge of the weather forecast}\label{SSS:DisturbancePerfect}
In this section we ran the simulations considering perfect knowledge of the disturbance over the horizon, obtaining the following results.}
\paragraph{Result 1} The comparison for temperature and input schedule obtained allowing small bound violations in DPC is shown in Figure \ref{F:comparison_small}. For sake of clarity, the simulation period is restricted to $4$ days and a half, from May $1$, $2016$ $00am$ to May $5$, $2016$ $1pm$. We can see that the temperature controlled with DPC does not violate the bounds and if it does then the violation is approximately $0.1\,\degree C$. Bang-bang control also presents small bounds violations due to its working principle. We can see how the DPC control law requires the heating system to be ON for less time than the bang-bang one to keep the temperature in the comfort range. 
We will see in Figure \ref{F:comparison_all_energy_E+} that this translates to significant energy saving.

@@

%\begin{figure}[h!]
%	\begin{center}
%		\includegraphics[width=26pc]{figures/Energy_all.eps}
%	\end{center}
%	\caption{Comparison of DPC and bang-bang control performance with different violations using random forest model.}
%	\label{F:comparison_all_energy}
%\end{figure}
%An alternative comparison can be done considering the EnergyPlus model of the house for energy consumption described in Section \ref{SS:energyPlusmodel}. Results are shown in Figure \ref{F:comparison_all_energy_E+}.
In Figure \ref{F:comparison_all_energy_E+}, using the thermal energy consumption model derived in Section \ref{SS:energyPlusmodel} using EnergyPlus, we show how DPC outperforms the bang-bang controller also in terms of energy consumption and how the bounds violations allow us to save more energy. In this case, since the plot is clear and we are interested in showing energy saving on a long period, we ran the simulations over the whole testing period, i.e. $15$ days of May, from May $1$, $2016$ to May $15$, $2016$. We observe that the energy consumption associated to the bang-bang control strategy is approximately equal to $177\,kWh$. If we want to keep the temperature within a comfort range, only allowing small violations, the use of DPC produce an energy saving of $45\, kWh$, that corresponds to the $25.4\%$ over a period of $15$ days. In case of medium violations get an energy saving of $57\, kWh$, that is $32.2\%$. Instead if we allow a large violation over the same period, the energy saving is of $87\, kWh$, that corresponds to the $49.2\%$.
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=28pc]{figures/Temperatures_all.eps}
	\end{center}
	\caption{Comparison, in terms of comfort, of DPC control performance simulated over $5$ days of the testing period with $3$ different violation configurations: small, medium and large. With the large violation configuration, the temperature is almost always outside of the lower bound when this is tighter. However the maximum bound violation is less than $1\degree C$. With the small violation configuration, the temperature is always within the bound with very few exceptions. However, when it happens, the violation is lower than $0.1\degree C$. The medium violation configuration gives a temperature bound violation that is in the middle with respect to the small and the large ones.}
	\label{F:comparison_all_temperature}
\end{figure}
\begin{table}[t!]
	\centering
	%	\scalebox{0.9}{
	\begin{tabular}{lccccc}
		\toprule
		CONTROLLER  & LBV $\mathrm{MBE}$  & LBV $\mathrm{RMSE}$ & UBV $\mathrm{MBE}$ & UBV $\mathrm{RMSE}$ 	\\ 
		\midrule
		$DPC-SV$    & $0.013$             & $0.028$  			      & $0$    				 & $0$     	  	\\
		$DPC-MV$    & $0.165$ 			  & $0.146$     			  & $0$    				 & $0$		  	\\
		$DPC-LV$    & $0.410$  			  & $0.224$     			  & $0$    				 & $0$	      	\\
		$Bang-bang$ & $0.049$ 			  & $0.080$    				  & $0.0063$ 		     & $0.0120$	  	\\
		\bottomrule
	\end{tabular}
	%	}
	\caption{Lower Bound Violation (LBV) and Upper Bound Violation (UBV) errors expressed as $\mathrm{MBE}\%$ and $\mathrm{CV(RMSE)}\%$ for DPC Small Violation (DPC-SV), DPC Medium Violation (DPC-MV), DPC large Violation (DPC-LV) and bang-bang controller.}
	\captionsetup{justification=centering}
	\label{T:violationErrors}
\end{table}
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=28pc]{figures/Energy_all_EnergyPlus.eps}
	\end{center}
	\caption{Comparison of DPC and bang-bang controller performance over $15$ days of the testing period with different violation configurations, in terms of thermal energy saving using EnergyPlus model. Using bang-bang controller the house energy consumption after $15$ days is of $177kWh$. DPC with small, medium and large violation configurations allows an energy saving of $25.4\%$, $32.3\%$ and $49.2\%$ respectively.}
	\label{F:comparison_all_energy_E+}
\end{figure}

\textcolor[rgb]{0,0,1}{
\subsubsection{Weather forecast subject to uncertainty}\label{SSS:DisturbanceUncertain}
In \cite{Petersen2014AE} the authors investigated, through a large-scale simulation study, the effect of weather forecast uncertainty on the performance of MPC in building systems operations, and compared to the performance of a rule-base strategy.
They considered 48 different scenarios of uncertainties on 72 hours weather forecasts.
On such long horizon, results have shown that, with few exceptions, MPC outperforms the rule based controller in case of energy savings and/or thermal indoor environment, and is in general quite close to the perfect forecast case, despite the uncertainty in weather forecast.}

\textcolor[rgb]{0,0,1}{Horizon length for the DPC algorithm presented in this paper is usually much shorter, as for example $6\ hours$ in Section \ref{S:proof}, $7\ hours$ in Section \ref{S:casestudy}, and $40\ minutes$ in Section \ref{S:realCaseStudy}. This means the weather forecast is more accurate than the 72 hours case presented in \cite{Petersen2014AE}, hence also control performance is even closer to the perfect knowledge forecast case.}

\textcolor[rgb]{0,0,1}{Nevertheless, to show the robustness of our approach, in this section we provide simulations considering noisy weather forecast.
To this aim, we add noises with normal distribution on the disturbance variables in $\tX^d$ used in the DPC problem \eqref{E:DPCrealcase}, i.e. the disturbance in input in the blue rectangle in Figure \ref{F:overview}, while we use the correct ones to simulate the process, i.e. the disturbance in input in the "Plant" box in the red rectangle in Figure \ref{F:overview}.
In Table \ref{T:NoiseParameters} we summarize the mean and the deviation values of the Gaussian noises that we add to each variable.
We obviously do not add any noise on the "Time of the day" and on the "Day of the week" since those are perfectly known.
In the table we also report the range of the values that the variables assumed during the reference period of the historical dataset.
This is to compare with the mean and deviation values we chose to show that we considered quite bad error on the forecast.
In the following results we show the change in performance on bounds violation and energy consumption due to the forecast inaccuracy.}
\begin{table}[t!]
	\centering	
	\textcolor[rgb]{0,0,1}{\begin{tabular}{lccc}
		\toprule
		Variable               & Range      & Mean & Deviation \\ 
		\midrule
		Outside temperature    & [0,31]     & 1	   & 0.5       \\
		Wind                   & [0,5] 		& 0.2  & 0.25      \\
		Atmospheric pressure   & [990,1030] & 50   & 50        \\
		Relative Humidity      & [20,91]	& 50   & 5         \\
		Solar Radiation        & [0,1000]   & 50   & 50        \\
		Time of the day        & [0,23]     & 0    & 0         \\
		Day of the week        & [1,7]      & 0    & 0         \\
		\bottomrule
	\end{tabular}}
	\caption{\textcolor[rgb]{0,0,1}{Mean and deviation values of the Gaussian noises added on the weather forecast data, and the range of variation of the variables in the historical dataset.}}
	\captionsetup{justification=centering}
	\label{T:NoiseParameters}
\end{table}

\textcolor[rgb]{0,0,1}{\paragraph{Result 1} In Figure \ref{F:ComparisonTempNoisy} a comparison of the DPC results in terms of temperature control, between the perfect and the noisy forecasts, is shown.
For the sake of plot's clarity, we considered 4 days and a half as simulative period and we split the plot into 3 sub-figures referring to the small, medium and large violation cases.
We can see that in the case of small and large violation we have a small deterioration in performance in terms of bounds violation, although this is more highlighted in the large violation case.
The medium violation cases are instead comparable.
The maximum violation, as in the case of perfect forecast, is still lower than $1\,\degree C$.
In particular, we report in Table \ref{T:violationErrorsNoisy} the violation errors in terms of MBE and CV(RMSE).
If we compare them with the ones in Table \ref{T:violationErrors}, we can see that the performance of DPC with noisy forecast are still good if compared with the performance of DPC with perfect forecast, despite the extremely bad prediction error that we considered on the weather forecast.
}
\begin{figure}[t!]
	\begin{center}
		\vspace{1.1cm}
		\subfigure{
			\label{F:SmallNoisy}
			\centering
			\includegraphics[width=23pc]{figures/Temperatures_small_noisy.eps}
		}	
		\subfigure{
			\label{F:MediumNoisy}
			\centering
			\includegraphics[width=23pc]{figures/Temperatures_medium_noisy.eps}
		}
		\subfigure{
			\label{F:LargeNoisy}
			\centering
			\includegraphics[width=23pc]{figures/Temperatures_large_noisy.eps}
		}	
	\end{center}
	\caption{\textcolor[rgb]{0,0,1}{Comparison of DPC considering perfect and noisy weather forecasts. Small, medium and large violation cases are compared.}}
	\captionsetup{justification=centering}
	\label{F:ComparisonTempNoisy}
\end{figure}

\begin{table}[t!]
	\centering
	%	\scalebox{0.9}{
	\textcolor[rgb]{0,0,1}{\begin{tabular}{lccccc}
		\toprule
		CONTROLLER  & LBV $\mathrm{MBE}$  & LBV $\mathrm{RMSE}$ & UBV $\mathrm{MBE}$ & UBV $\mathrm{RMSE}$ 	\\ 
		\midrule
		$DPC-SV$    & $0.072$             & $0.074$  			      & $0$    				 & $0$     	  	\\
		$DPC-MV$    & $0.168$ 			  & $0.13$       			  & $0$    				 & $0$		  	\\
		$DPC-LV$    & $0.708$  			  & $0.343$     			  & $0$    				 & $0$	      	\\
		\bottomrule
	\end{tabular}}
	%	}
	\caption{\textcolor[rgb]{0,0,1}{Lower Bound Violation (LBV) and Upper Bound Violation (UBV) errors expressed as $\mathrm{MBE}\%$ and $\mathrm{CV(RMSE)}\%$ for DPC Small Violation (DPC-SV), DPC Medium Violation (DPC-MV), DPC large Violation (DPC-LV) and bang-bang controller, considering noisy weather forecast.}}
	\captionsetup{justification=centering}
	\label{T:violationErrorsNoisy}
\end{table}

\textcolor[rgb]{0,0,1}{\paragraph{Result 2} 
In Figure \ref{F:comparison_all_energy_E+_noisy}, we show the difference in terms of energy consumption considering the perfect weather forecast and the noisy one.
We can observe the case with imperfect forecast is very close to the perfect forecast case, and depending the conditions for which the disturbance is over or underestimated, we have more or less energy consumption. These results shows the strong robustness of the DPC with respect to errors in the weather forecast.}
\begin{figure}[t!]
	\begin{center}
		\includegraphics[width=28pc]{figures/Energy_all_EnergyPlus_noisy.eps}
	\end{center}
	\caption{\textcolor[rgb]{0,0,1}{Comparison of DPC in terms of thermal energy saving using EnergyPlus model, considering perfect (full) and imperfect (dashed) weather forecast, over $15$ days of the testing period with different violation configurations. The performance are pretty similar, showing the potential robustness of DPC.}}
	\label{F:comparison_all_energy_E+_noisy}
\end{figure}

### 2018-01-18 paper/final/conclusion.tex
Introduction and noisy forecast

To overcome the difficulties associated with the model identification in Model Predictive Control (MPC), we introduce a novel idea for predictive control using data: Data Predictive Control (DPC). Data-based control strategies are usually based on non-physical models, therefore the can not be integrated with most of the classical control approaches. The goal is to create data-driven models that are suitable for receiding horizon control. To this aim, we present two algorithms, based on trees and random forests, to create data-driven models to be used in the DPC strategy. We then apply DPC to $3$ different case study in order to prove its strength.
\begin{enumerate}
\item \emph{\textbf{Comparison with MPC}} We compare the performance of our Data Predictive Control to MPC on a multivariable bilinear building model. We establish that DPC with random forests shows a remarkable similarity to MPC in the optimal control strategies explaining $70\%$ variance. On the other hand, DPC with regression trees suffers from practical limitations due to model overfitting.
\item \emph{\textbf{Demand Response application}} We further apply DPC with random forests to a large scale 6 story EnergyPlus model with 22 zones for which the traditional model-based control is largely unsuitable due to complex dynamics and the cost of model identification. We show that DPC, relying only on the sensor data, can provide significant energy savings while maintaining thermal comfort. Our results demonstrate that even for such complex system, DPC tracks a reference signal with a mean error of $3\%$.
\item \emph{\textbf{Optimal heating system scheduling of a real house}} We finally apply DPC using data from a real house and compare it with the classical bang-bang controller widely used for temperature control in houses. We implemented DPC to guarantee energy saving while guaranteeing thermal comfort for the occupants. With respect to a bang-bang controller, we obtained an energy saving that goes from $25.4\%$, when we force the temperature to be strictly in a comfort range, to $49.2\%$, if we allow small violations.
\end{enumerate}
DPC has applications which go beyond buildings and energy systems, to industrial process control, and controlling large critical infrastructures like water networks, district heating \& cooling. DPC is immensely valuable in situations where first principles based modeling cost is extremely high.

>>>>

To overcome the difficulties associated with the model identification in Model Predictive Control (MPC), we introduce a novel idea for predictive control using data: Data Predictive Control (DPC). Data-based control strategies are usually based on non-physical models, therefore the can not be integrated with most of the classical control approaches. The goal is to create data-driven models that are suitable for receiding horizon control. To this aim, we present two algorithms, based on trees and random forests, to create data-driven models to be used in the DPC strategy. We then apply DPC to $3$ different case study in order to prove its strength.
\begin{enumerate}
\item \emph{\textbf{Comparison with MPC}} We compare the performance of our Data Predictive Control to MPC on a multivariable bilinear building model. We establish that DPC with random forests shows a remarkable similarity to MPC in the optimal control strategies explaining $70\%$ variance. On the other hand, DPC with regression trees suffers from practical limitations due to model overfitting.
\item \emph{\textbf{Demand Response application}} We further apply DPC with random forests to a large scale 6 story EnergyPlus model with 22 zones for which the traditional model-based control is largely unsuitable due to complex dynamics and the cost of model identification. We show that DPC, relying only on the sensor data, can provide significant energy savings while maintaining thermal comfort. Our results demonstrate that even for such complex system, DPC tracks a reference signal with a mean error of $3\%$.
\item \emph{\textbf{Optimal heating system scheduling of a real house}} We finally apply DPC using data from a real house and compare it with the classical bang-bang controller widely used for temperature control in houses. We implemented DPC to guarantee energy saving while guaranteeing thermal comfort for the occupants. With respect to a bang-bang controller, we obtained an energy saving that goes from $25.4\%$, when we force the temperature to be strictly in a comfort range, to $49.2\%$, if we allow small violations.
\end{enumerate}

DPC has applications which go beyond buildings and energy systems, to industrial process control, and controlling large critical infrastructures like water networks, district heating \& cooling. DPC is immensely valuable in situations where first principles based modeling cost is extremely high.
